---
title: "Simulation"
author: "Sajal Shrestha"
date: "7/21/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Write R programs for simulations from probability models and randomization-based experiments

-   I can write R programs for simulations from probability models

    -   I can apply a function to groupings within a data source.
    -   I can use common probability distributions to simulate data and explore statistical ideas.

-   I can write R programs for randomization-based experiments

    -   I can apply a function to groupings within a data source.
    -   I can implement resampling methods to make conclusions about data.

```{r load-package}
library(tidyverse)
```
```{r storms-dataset}
head(storms)
```

```{r}
# Data overview

mean(storms$pressure)
sd(storms$pressure)
```

```{r storm-pressure-simulation}
pressure_samp_1000 <- tibble(
  values = rnorm(n = 1000, mean = 990, sd = 19)
)
pressure_samp_1000$values

```

```{r}
summary(pressure_samp_1000$values)
```

```{r}
ggplot(pressure_samp_1000, aes(x = values)) +
  geom_histogram(
    aes(y = ..count.. / sum(..count..)),
    fill = "white",
    color = "black",
    binwidth = 3
  ) +
  stat_function(
    fun = function(x)
      dnorm(x, mean = 990, sd = 19) * 3,
    color = "#0065a4",
    size = 2,
    alpha = 0.4
  ) +
  geom_vline(
    xintercept = mean(pressure_samp_1000$values),
    color = "#a43f00",
    size = 2
  ) +
  theme_minimal() +
  labs(y = "proportion")
```

```{r}
ggplot(pressure_samp_1000, aes(y=values)) + 
  geom_boxplot()
```

